---
title: "Simple document"
author: 'Lu Qiu'
date: '2023-09-12'
output: github_document
---


```{r, echo=FALSE, message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1: First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```
The mean of the sample is `r round(mean(samp), digit =4)`

# Section 2: Make a plot

This code is borrowed from last lecture; it creates a dataframe for plotting.

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000),
    y2 = 1 + 2 * x + 4 * x^2 + rnorm(1000)
  )
```


Next up is a histogram of the `x` variable in the `plot_df`.

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Lastly, I will do a scatterplot.

```{r}
ggplot(plot_df, aes(x = x , y = y)) + geom_point()
```
Here's a list:

* This is a list
* This is another list

# Section 3: Learning assessment

The chunk below creates a dataframe containing a sample of size 500 from a  random normal variable, constructs the specified logical vector, takes the absolute value of each element of that sample,and produces a histogram of the absolute value. The code chunk also finds the median of the sample and stores it for easy in-line printing.

```{r la_df}
la_df = 
  tibble(
    norm_samp = rnorm(500, mean = 1),
    log_vec = norm_samp >= 0,
    abs_norm_samp = abs(norm_samp)
  )
ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

```

# Section 4: Text formatting 


*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell




